Algebraic filtering of surfaces from medical images with Julia

### 2019-12-31 src/paper.tex
code highlititing

% M. Jirik added - code highlithing
% \usepackage{minted}
\usepackage[cache=false]{minted}
% \usepackage{minted}
%SetFonts

@@

\begin{verbatim}
using Distributed
addprocs(3)
using LarSurf

LarSurf.lsp_setup([20, 20, 20]) # set the block size

segmentation = LarSurf.generate_truncated_sphere(10)
V, FV = LarSurf.lsp_get_surface(segmentation)
FVtri = LarSurf.triangulate_quads(FV)
Vs = LarSurf.Smoothing.smoothing_FV_taubin(V, FV, 0.4, -0.3, 50)

objlines = LarSurf.Lar.lar2obj(Vs, FVtri, "truncated_sphere_tri_taubin.obj")
\end{verbatim}

We include more examples of extracted surfaces based on Micro-CT data of corrosion casts of pig liver.
\cite{eberlova2017use}.
% The resolution
Lar-surf

\begin{minted}{python}

using Pkg
\end{minted}
% \begin{minted}[breaklines,escapeinside=||,mathescape=true, linenos, numbersep=3pt, gobble=2, frame=lines, fontsize=\small, framesep=2mm]{julia}
% Your awesome julia code here\end{minted}

>>>>

%%%%%%% M. Jirik added - code highlithing
% \usepackage{minted}
% \usepackage[cache=false]{minted}
\usepackage{listings}
% \usepackage{minted}
%SetFonts
\lstdefinelanguage{Julia}%
  {morekeywords={abstract,break,case,catch,const,continue,do,else,elseif,%
      end,export,false,for,function,immutable,import,importall,if,in,%
      macro,module,otherwise,quote,return,switch,true,try,type,typealias,%
      using,while},%
   sensitive=true,%
   alsoother={$},%
   morecomment=[l]\#,%
   morecomment=[n]{\#=}{=\#},%
   morestring=[s]{"}{"},%
   morestring=[m]{'}{'},%
}[keywords,comments,strings]%

\lstset{%
    language         = Julia,
    basicstyle       = \ttfamily,
    keywordstyle     = \bfseries\color{blue},
    stringstyle      = \color{magenta},
    % commentstyle     = \color{ForestGreen},
    commentstyle     = \color{green},
    showstringspaces = false,
}
%%%%%%

@@

% \begin{verbatim}
% \begin{lstlisting}
% using Distributed
% addprocs(3)
% using LarSurf
% LarSurf.lsp_setup([20, 20, 20])

% segmentation = LarSurf.generate_truncated_sphere(10)
% V, FV = LarSurf.lsp_get_surface(segmentation)
% FVtri = LarSurf.triangulate_quads(FV)
% Vs = LarSurf.Smoothing.smoothing_FV_taubin(V,FV,0.4,-0.3,50)

% objlines = LarSurf.Lar.lar2obj(Vs, FVtri, "tri_taubin.obj")
% \end{lstlisting}
% \end{verbatim}
We include more examples of extracted surfaces based on Micro-CT data of corrosion casts of pig liver.
\cite{eberlova2017use}.
The size of the visualized data is $100\times100\times100$ voxels. The number of of triangles is 
544784 and number of vertices is 272826.

% The resolution
% 
% pth = Pio3d.datasets_join_path("medical/orig/3Dircadb1.1/MASKS_DICOM/liver")
\begin{lstlisting}[caption=Read from DICOM files]
using Distributed
using Pio3d
addprocs(3)  # set number of processors
using LarSurf

LarSurf.lsp_setup([64, 64, 64])  # set block size

# read data
datap = Pio3d.read3d("3Dircadb1.1/MASKS_DICOM/liver")
segmentation = datap["data3d"]
voxelsize_mm = datap["voxelsize_mm"]

# get surface
V, FV = LarSurf.lsp_get_surface(segmentation, voxelsize_mm)
FVtri = LarSurf.triangulate_quads(FV)

# do smoothing and save data
Vs = LarSurf.Smoothing.smoothing_FV_taubin(V,FV,0.5,-0.2,40)
objlines = LarSurf.Lar.lar2obj(Vs, FVtri, "liver.obj")
\end{lstlisting}

% \begin{minted}{python}

% using Pkg
% \end{minted}
% \begin{minted}[breaklines,escapeinside=||,mathescape=true, linenos, numbersep=3pt, gobble=2, frame=lines, fontsize=\small, framesep=2mm]{julia}
% Your awesome julia code here\end{minted}
